---
title             : "YOUR PAPER TITLE"
shorttitle        : "YOUR SHORT TITLE"
date              : "`r format(Sys.time(), '%B %d, %Y')`"

author: 
  - name          : "YOUR NAME"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "YOUR ADDRESS"
    email         : "YOUR@EMAIL-ADDRESS.COM"
    # role: 
    #   - Conceptualization
    #   - Writing - Original Draft Preparation
    #   - Writing - Review & Editing
    #   - Coding of analyses and visualization
  - name          : "YOUR CO-AUTHOR"
    affiliation   : "2,3"
    # role:
    #   - Conceptualization
    #   - Writing - Original Draft Preparation
    #   - Writing - Review & Editing
    #   - Coding of analyses and visualization
  - name          : "YOUR OTHER CO-AUTHOR"
    affiliation   : "2"
    # role:
    #   - Conceptualization & Framing
    #   - Writing - Original Draft Preparation
    #   - Writing - Review & Editing
    #   - Visualization

affiliation:
  - id            : "1"
    institution   : "Language Science, University of HERE, STATE"
  - id            : "2"
    institution   : "Brain and Cognitive Sciences, University of THERE"
  - id            : "3"
    institution   : "Computer Science, University of THERE"

authornote: |
  We are grateful to ### ommitted for review ###
# list all your acknowledgments here. Do so early, and whenever somebody has helped you. Lead by example and acknowledge the inputs, sources, and generosity of other researchers. 

abstract: |
  YOUR ABSTRACT GOES HERE. All data and code for this study are shared via OSF, including the R markdown document that this article is generated from, and an R library that implements the models we present.
  
keywords          : "KEY-WORD1; KEY-WORD2; KEY-WORD3; ..."
wordcount         : "X"

bibliography      : ["latex-stuff/library.bib", "latex-stuff/r-references.bib"]
link-citations    : yes
csl               : latex-stuff/apa-6th-edition.csl

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
numbersections    : true
mask              : no
draft             : yes

header-includes: 
 - \usepackage{sectsty}
 - \usepackage{animate}
 - \usepackage{amsmath}
 - \usepackage{tikz}
 - \usetikzlibrary{bayesnet}
 - \usepackage{booktabs}
 - \usepackage{subfig}
 - \usepackage{tablefootnote}
 - \usepackage{float}
 - \usepackage{placeins}
 - \usepackage{xcolor}
 - \sectionfont{\color{black}}
 - \subsectionfont{\color{black}}
 - \subsubsectionfont{\color{black}}
 - \usepackage{setspace}\doublespacing
 
documentclass     : "apa6"
classoption       : "man"
fontsize          : 11pt
output: 
  papaja::apa6_pdf:
    extra_dependencies:
      "subfig"
    latex_engine: xelatex
    includes:
      in_header: latex-stuff/header.tex
    keep_tex: yes
    # citation_package: default # natbib, biblatex
always_allow_html: true
---

\setcounter{secnumdepth}{5}

<!-- THIS IS THE DOCUMENT THAT YOU USE FOR KNITTING. IT WILL KNIT ALL THE OTHER SECTIONS, TOO -->

```{r, include=FALSE, message=FALSE}
if (!exists("PREAMBLE_LOADED")) source("preamble.R")
```

```{r knitr-setup, include=FALSE}
# To keep figure sizes comparable across the paper, you can define a basic width and height (e.g., for each panel)
# and then refer to those variables in the knitr chunk options that describe the figure width and height for a 
# specific R chunk.
options(width = 200, digits = 2, OutDec = ".", tinytex.verbose = TRUE)
base.width = 2.15
base.height = 2.15

knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = TRUE, 
  results = "markup", cache = TRUE,
  interval = .2,
  fig.path = "../figures/knitted/", fig.align = "center", fig.height = 2.5, fig.width = 2.5)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})

# Some useful formatting for warnings and error messages, so that they are not easily missed.
knitr::knit_hooks$set(document = function(x) {sub('\\usepackage[]{color}', '\\usepackage{xcolor}', x, fixed = TRUE)})
color_block = function(color) { function(x, options) sprintf('\\color{%s}\\begin{verbatim}%s\\end{verbatim}\\color{black}', color, x) }
knitr::knit_hooks$set(error = color_block('red'))
knitr::knit_hooks$set(warning = color_block('orange'))
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r}
INCLUDE_TODO = T            # switch on/off to get to do list.
```

```{r, child="section-TO-DO.Rmd", eval= if (INCLUDE_TODO) TRUE else FALSE}
```

\newpage 
\setcounter{page}{1}
\setcounter{section}{0}

<!-- Do NOT knit this document. It is part of a larger document. Instead knit the main document (my-apa-formatted-article) -->

# Defining a generative model of flight paths
For now, we're generated some fake flight data to illustrate the model. We'll replace this with real data later. Set `echo=TRUE` to see the code in the knitted PDF.

```{r make-fake-data}
# start and endpoints
start <- c(0, 0)

# weights (theta) and precision (kappa)
theta <- c(goal = 0.19, social = 0.18, memory = 0.31)
theta["continuity"] <- 1 - sum(theta)
kappa <- c(goal = 1.54, social = 2.18, memory = 0, continuity = 8.69)

n_experiment <- 1
n_pigeon <- 1
n_generation <- 1
n_flight <- 12
n_time <- 150
n_landmark.mu <- 25

# Functions
get_next_landmark <- function(position, landmarks, goal, viewing_distance = 1.2) {
  distance_to_goal <- sqrt(sum(position - goal)^2)
  landmarks %<>%
    mutate(
      distance_to_position = sqrt(rowSums(landmarks[, c("x", "y")] - position)^2),
      visible = distance_to_position < viewing_distance) %>%
    filter(visible)
  
  if (nrow(landmarks) == 0) {
    return(NA) 
  } else { 
    return(
      landmarks %>%
        filter(distance_to_goal == min(distance_to_goal)) %>%
        pull(ID))
  }
}

d.sim <- tibble()
for (e in 1:n_experiment) { # experiments (different goal locations)
  distance <- 10
  finish.heading <- runif(1, -pi, pi)
  finish <- c(cos(finish.heading), sin(finish.heading)) * distance
  
  # For now: constant speed within and across pigeons
  velocity <- distance / n_time * 5
  # When have pigeons arrived?
  arrived_when.resolution <- distance / 50
  
  d <- 
    crossing(
      pigeon = 1:n_pigeon, generation = 1:n_generation, flight = 1:n_flight, time = 1:n_time, 
      position.x = start[1], position.y = start[2], velocity = velocity,
      position.partner.x = start[1], position.partner.y = start[2], velocity.partner = velocity,
      goal.x = finish[1], goal.y = finish[2]) %>%
    mutate(
      # FOR NOW: assume pigeon's partners have flown equally often
      flight.other = flight,
      # initialize with random headings
      heading = runif(1, -pi, pi),
      heading.partner = runif(1, -pi, pi),
      next_heading = runif(1, -pi, pi),
      next_heading.partner = runif(1, -pi, pi))
  
  # Make some landmarks spread out over the space surrounding the start and goal
  n_landmark <- rpois(1, n_landmark.mu)
  d.landmarks <- 
    tibble(ID = 1:n_landmark) %>%
    mutate(
      x = runif(n(), min(finish[1] * c(-1.3, 1.3)),  max(finish[1] * c(-0.5, 1.5))),
      y = runif(n(), min(finish[2] * c(-1.3, 1.3)),  max(finish[2] * c(-0.5, 1.5))),
      distance_to_goal = sqrt((x - finish[1])^2 + (y - finish[2])^2))
  
  for (p in 1:n_pigeon) { # pigeon
    for (g in 1:n_generation) { # generation
      for (f in 1:n_flight) { # flight within generation
        message("Processing pigeon ", p, " in generation ",  g, " on flight ", f)
        
        for (t in 1:n_time) { # time within flight
          d.sim %<>%
            bind_rows(
              within(
                d[d$pigeon == p & d$generation == g & d$flight == f & d$time == t,],
                {   
                  if (time != 1) {
                    # Get new position and heading given heading decision and velocity from previous time point
                    heading = d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$next_heading
                    position.x = d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$position.x + 
                      d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$velocity * cos(heading)
                    position.y = d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$position.y + 
                      d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$velocity * sin(heading)
                    
                    heading.partner = d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$next_heading.partner
                    position.partner.x = d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$position.partner.x + 
                      d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$velocity.partner * cos(heading.partner)
                    position.partner.y = d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$position.partner.y + 
                      d.sim[d.sim$pigeon == p & d.sim$generation == g & d.sim$flight == f & d.sim$time == t - 1,]$velocity.partner * sin(heading.partner)
                  }
                  
                  # Check whether pigeon has arrived at goal
                  distance_to_goal = sqrt((goal.x - position.x)^2 + (goal.y - position.y)^2)
                  distance_to_goal.partner = sqrt((goal.x - position.partner.x)^2 + (goal.y - position.partner.y)^2)
                  if (distance_to_goal < arrived_when.resolution) {
                    velocity = 0
                  }
                  if (distance_to_goal.partner < arrived_when.resolution) {
                    velocity.partner = 0
                  }
                  
                  # Get plans of pigeon for next time step
                  # Get goal-dependent target heading
                  mu_goal = atan2(goal.y - position.y, goal.x - position.x)
                  
                  # Estimate partner's next position and get other-dependent target heading
                  position.expected_partner.x = position.partner.x + velocity.partner * cos(heading.partner)
                  position.expected_partner.y = position.partner.y + velocity.partner * sin(heading.partner)
                  mu_other = atan2(position.expected_partner.y - position.y, position.expected_partner.x - position.x)
                  
                  closest_landmark <- get_next_landmark(c(position.x, position.y), d.landmarks, c(goal.x, goal.y))
                  if (!is.na(closest_landmark)) {
                    position.closest_next_landmark.x <- d.landmarks[d.landmarks$ID == closest_landmark,]$x
                    position.closest_next_landmark.y <- d.landmarks[d.landmarks$ID == closest_landmark,]$y
                    mu_memory = atan2(position.closest_next_landmark.y - position.y, position.closest_next_landmark.x - position.x)
                    
                    # Need to implement more realistic memory + threshold distance at which landmarks can be seen
                    # (with this memory model pigeons gets stuck on landmarks, when those landmarks are not conveniently
                    # located in uniform steps along the start-to-goal line)
                    kappa["memory"] <<- 
                      case_when(
                        flight == 1 ~ 0,
                        flight == 2 ~ 0.27,
                        flight == 3 ~ 0.58,
                        flight == 4 ~ 1.11,
                        flight == 5 ~ 2.18,
                        TRUE ~ 6.78)
                  } else {
                    # when there is no visible landmark ignore memory
                    mu_memory <- 0
                    kappa["memory"] <<- 0
                  }

                  # Draw random samples from each of the von Mises distribution
                  a_goal = rvon_mises(1, mu = mu_goal, kappa = kappa["goal"])
                  a_other = rvon_mises(1, mu = mu_other, kappa = kappa["social"])
                  a_memory = rvon_mises(1, mu = mu_memory, kappa = kappa["memory"])
                  a_continuity = rvon_mises(1, mu = heading, kappa = kappa["continuity"])
                  
                  # Determine next heading
                  next_heading = 
                    atan2(
                      theta["goal"] * sin(a_goal) +
                        theta["social"] * sin(a_other) +
                        theta["memory"] * sin(a_memory) +
                        theta["continuity"] * sin(a_continuity),
                      theta["goal"] * cos(a_goal) +
                        theta["social"] * cos(a_other) +
                        theta["memory"] * cos(a_memory) +
                        theta["continuity"] * cos(a_continuity))
                  
                  # Same for partner
                  mu_goal.partner = atan2(goal.y - position.partner.y, goal.x - position.partner.x)
                  position.expected.x = position.x + velocity * cos(heading)
                  position.expected.y = position.y + velocity * sin(heading)
                  mu_other.partner = atan2(position.expected.y - position.partner.y, position.expected.x - position.partner.x)
                  
                  closest_landmark.partner <- get_next_landmark(c(position.partner.x, position.partner.y), d.landmarks, c(goal.x, goal.y))
                  if (!is.na(closest_landmark.partner)) {
                    position.partner.closest_next_landmark.x <- d.landmarks[d.landmarks$ID == closest_landmark.partner,]$x
                    position.partner.closest_next_landmark.y <- d.landmarks[d.landmarks$ID == closest_landmark.partner,]$y
                    mu_memory.partner <- 
                      atan2(
                        position.partner.closest_next_landmark.y - position.partner.y, 
                        position.partner.closest_next_landmark.x - position.partner.x)
                    
                    # Need to implement more realistic memory + threshold distance at which landmarks can be seen
                    # (with this memory model pigeons gets stuck on landmarks, when those landmarks are not conveniently
                    # located in uniform steps along the start-to-goal line)
                    kappa["memory.other"] <<- 
                      case_when(
                        flight == 1 ~ 0,
                        flight == 2 ~ 0.27,
                        flight == 3 ~ 0.58,
                        flight == 4 ~ 1.11,
                        flight == 5 ~ 2.18,
                        TRUE ~ 6.78)
                  } else {
                    # when there is no visible landmark ignore memory
                    mu_memory.partner <- 0
                    kappa["memory.other"] <<- 0
                  }
                  
                  a_goal.partner = rvon_mises(1, mu = mu_goal.partner, kappa = kappa["goal"])
                  a_other.partner = rvon_mises(1, mu = mu_other.partner, kappa = kappa["social"])
                  a_memory.partner = rvon_mises(1, mu = mu_memory.partner, kappa = kappa["memory.other"])
                  a_continuity.partner = rvon_mises(1, mu = heading.partner, kappa = kappa["continuity"])
                  next_heading.partner = 
                    atan2(
                      theta["goal"] * sin(a_goal.partner) +
                        theta["social"] * sin(a_other.partner) +
                        theta["memory"] * sin(a_memory.partner) +
                        theta["continuity"] * sin(a_continuity.partner),
                      theta["goal"] * cos(a_goal.partner) +
                        theta["social"] * cos(a_other.partner) +
                        theta["memory"] * cos(a_memory.partner) +
                        theta["continuity"] * cos(a_continuity.partner))
                  
                  # Remove what we don't need
                }))
        }
      }
    }
  }
}
``` 

## Visualizing flight paths

```{r plot-data, fig.show="animate", interval=1/10, fig.width=10, fig.height=10}
d.sim %>%
  ggplot() +
  geom_path(aes(position.x, position.y, group = flight, color = as.factor(flight)), linetype = 1,) +
  geom_path(aes(position.partner.x, position.partner.y, group = flight, color = as.factor(flight)), linetype = 2) +
  annotate("point", x = start[1], y = start[2], color = "green", shape = 1, size = 2) +
  annotate("point", x = finish[1], y = finish[2], color = "red", shape = 1, size = 2) +
  geom_point(data = d.landmarks, aes(x, y), color = "black", shape = 4) +
  scale_color_viridis_d("Flight") +
  coord_fixed() +
  facet_wrap(flight ~ pigeon)

d.sim %>%
  ggplot() +
  geom_point(aes(position.x, position.y, group = flight, color = as.factor(flight)), shape = 2, size = .8) +
  geom_point(aes(position.partner.x, position.partner.y, group = flight, color = as.factor(flight)), shape = 3, size = .8) +
  annotate("point", x = start[1], y = start[2], color = "green", shape = 1, size = 2) +
  annotate("point", x = finish[1], y = finish[2], color = "red", shape = 1, size = 2) +
  geom_point(data = d.landmarks, aes(x, y), color = "black", shape = 4) +
  scale_color_viridis_d("Flight") +
  coord_fixed() +
  facet_wrap(flight ~ pigeon) +
  theme_minimal() +
  transition_states(time) +
  shadow_wake(wake_length = 1) +
  labs(title = "Time: {closest_state}")
```

# Load first flight data

```{r load-first-flights}
GOAL <- c(616070, 5738228)
d <- tibble()

for (f in list.files("../data/SpeedConvergence/", pattern = "*.csv", full.names = TRUE, recursive=TRUE)) {
  d %<>% bind_rows(read_csv(f) %>% 
                     mutate(flight = f))
}


# Down sample data to 0.5Hz
d %<>% 
  group_by(flight) %>%
  filter(row_number() %% 10 == 0) %>%
  ungroup()

d %<>% 
  rename(x = easting, y=northing, t=time) %>%
  select(x, y, t, flight) %>%
  group_by(flight) %>%
  mutate(
    next_heading=atan2(lead(y, 1)-y, lead(x, 1)-x),
    heading=lag(next_heading, 1)) %>%
  ungroup() %>%
    mutate(
      mu_goal=atan2(GOAL[2]-y, GOAL[1]-x),
      distance_to_goal=sqrt((GOAL[1]-x)^2 + (GOAL[2]-y)^2),
      distance_to_goal=(distance_to_goal-mean(distance_to_goal))/(2*sd(distance_to_goal))
      )

# Removing NAs manually
d %<>% 
  filter(!is.na(heading)) %>%
  filter(!is.na(next_heading))

d %>%
  ggplot(aes(x, y, color=flight)) + 
  geom_path(aes(group=flight)) + 
  theme(legend.position="none")

d %>%
  ggplot(aes(t, mu_goal, color=flight)) + 
  geom_line(aes(group=flight)) + 
  theme(legend.position="none")
```


# Fitting a model to the data
This section defines a Bayesian mixture of van Mises model. Set `echo=TRUE` to see the code in the knitted PDF.

```{r bmm-priors}
# my_priors <- 
#   c(
#     prior(student_t(3, 0, 2.5), b, dpar = mu1),
#     prior(student_t(3, 0, 2.5), b, dpar = mu2),
#     prior(student_t(3, 0, 2.5), b, dpar = mu3),
#     prior(student_t(3, 0, 2.5), b, dpar = mu4),
#     prior(student_t(3, 0, 2.5), b, dpar = kappa1),
#     prior(student_t(3, 0, 2.5), b, dpar = kappa2),
#     prior(student_t(3, 0, 2.5), b, dpar = kappa3),
#     prior(student_t(3, 0, 2.5), b, dpar = kappa4),
#     prior(student_t(3, 0, 2.5), b, dpar = theta1),
#     prior(student_t(3, 0, 2.5), b, dpar = theta2),
#     prior(student_t(3, 0, 2.5), b, dpar = theta3))
my_priors <- 
  c(
    # prior(student_t(3, 0, 2.5), b, dpar = mu1),
    # prior(student_t(3, 0, 2.5), b, dpar = mu2),
    prior(student_t(3, 0, 2.5), b, dpar = kappa1),
    prior(student_t(3, 0, 2.5), b, dpar = kappa2),
    prior(student_t(3, 0, 2.5), b, dpar = theta1))
```

```{r bmm-fit}
# From https://stackoverflow.com/questions/32370485/convert-radians-to-degree-degree-to-radians
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}

# Useful discourse: https://discourse.mc-stan.org/t/modelling-circular-data-with-brms-gaussian-or-von-mises/26980/5
m <- 
  brm(
    formula = 
      bf(
        next_heading ~ 1,
        # Goal direction
        mu1 ~ 0 + offset(mu_goal),
        # kappa1 ~ 1, # 1 + (1 | flight) # In case we assume that the kappa is different for each pigeon/flight.
        kappa1 ~ 1 + s(distance_to_goal),
        theta1 ~ 1 + s(distance_to_goal) + (1 | flight),
        # Social direction
        # mu2 ~ 0 + offset(mu_other),
        # kappa2 ~ 1,
        # theta2 ~ 1,
        # Closest landmark direction
        # mu3 ~ 0 + offset(mu_memory),
        # kappa3 ~ 1,
        # theta3 ~ 1,
        # Continuity direction
        mu2 ~ 0 + offset(heading),
        kappa2 ~ 1),
    data = 
      # TO DO: go to long format to use the data from both pigeons
      d,
    family = 
      mixture(
        # Discussion of tan_half link which constrains the von Mises distribution to the interval [-pi, pi]
        # https://discourse.mc-stan.org/t/von-mises-distribution-tan-half-link/22182/2
        # Here, we're using the identity link since next_heading is already in radians
        von_mises(link = "identity", link_kappa = "log"), 
        nmix = 2,
        order = "none"),
    sample_prior = "yes",
    # Save the file. NOTE that this MIGHT requires deleting the file if one wants the model to be refit
    # (though the refit "on_change" option should take care of that)
    file = "../models/von-mises-2component-model", file_refit = "on_change",
    chains = 4, warmup = 1000, iter = 2000, control = list(adapt_delta = .9),
    cores = 4, threads = threading(2))
```

## Visualizing the posterior predictive
Figure \@ref(fig:bmm-validation show) shows the posterior predictive check for the fitted model.

(ref:bmm-validation) Posterior predictive of fitted model. The dashed line represents 45 degrees heading (it would make more sense to reformat the data to show heading relative to goal? ... MORE HERE

```{r bmm-validation, fig.cap="(ref:bmm-validation)"}
# Get the average goal heading from the start position and add it to pp check plot
START <- d %>%
  group_by(flight) %>%
  arrange(t) %>%
  summarise(across(c(x, y), first)) %>%
  summarise(across(c(x, y), mean)) %>%
  as.numeric()

pp_check(m, ndraws = 10) +
  geom_vline(xintercept = atan2(GOAL[2]-START[2], GOAL[1]-START[1]), linetype = 2)
```

```{r bmm-results}
summary(m)
conditional_effects(m)
plot(conditional_smooths(m), ask = F)
```

```{r}
# Get the MAP parameter estimates
f <-
  fixef(m) %>%
  as_tibble() %>%
  bind_rows(tibble(Estimate = 0)) %>%
  mutate(
    PredictorType = c(rep("kappa", 4), rep("theta", 4)),
    Predictor = 
      c(
        paste("kappa", c("goal", "social", "memory", "continuity"), sep = "_"), 
        paste("theta", c("goal", "social", "memory", "continuity"), sep = "_")),
    across(
      c(Estimate, Q2.5, Q97.5),
      ~ ifelse(PredictorType == "kappa", exp(.x), .x))) 

# transform the theta weights from log-odds into probabilities
f[5:8, "Estimate"] <- pmlogis_last(f[5:7, ]$Estimate)
f[5:8, "Q2.5"] <- pmlogis_last(f[5:7, ]$Q2.5)
f[5:8, "Q97.5"] <- pmlogis_last(f[5:7, ]$Q97.5)
# NOTE: the final weight the upper/lower intervals are swapped (by necessity).
f %<>% select(-Est.Error)

print(f)
```


Adding one citation example [@burkner2019].

```{r, child="section-references.Rmd", eval=T}
```

```{r, child="supplementary-information.Rmd", eval=T}
```
