\newpage
\renewcommand{\thesection}{\S \arabic{section}}

<!-- Do NOT knit this document. It is part of a larger document. Instead knit the main document (my-apa-formatted-article) 
     If you want to separate the SI from the rest of the paper, we recommend you do so AFTER knitting them into a single PDF. 
     This will make sure that all references to sections, figures, tables, etc. are working as intended. You can easily separate 
     the PDF into two parts, using e.g., Acrobat PDF viewer. //-->
     
# Supplementary information {-}
\setcounter{section}{1}

Both the main text and these supplementary information (SI) are derived from the same R markdown document available via [OSF](https://osf.io/q7gjp/). It is best viewed using Acrobat Reader. Some links and animations might not work in other PDF viewers. 

# Required software {#sec:SI-software}
The document was compiled using \texttt{knitr} [@xie2021] in RStudio with R:

```{r} 
version
```

You will also need to download the IPA font [SIL Doulos](https://software.sil.org/doulos/download/) and a Latex environment like (e.g., [MacTex](https://tug.org/mactex/mactex-download.html) or the R library \texttt{tinytex}). 

We used the following R packages to create this document: `r cite_r("latex-stuff/r-references.bib", withhold = T, pkgs = c("MVBeliefUpdatr"))`. If opened in RStudio, the top of the R markdown document should alert you to any libraries you will need to download, if you have not already installed them. The full session information is provided at the end of this document.

# Other sections

# Session Info

```{r session_info, echo=FALSE, results='markup'}
devtools::session_info()
```

